Cytokine analysis script - all rounds - adjusted for tissue weight

### 2022-11-19 code/Round 4/Gene expression.Rmd
progress

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

#### Gene expression

```{r}
delta_gene_expr <- read_excel("data/processed/gene_expression_fold_changes.xlsx")

bar_charts_all_genes <- delta_gene_expr %>% 
  mutate(
    groups = recode_factor(  #Change the order of the groups to desired plot order
      groups,
      "con-bf"= "CON-BF",
      "fvt-form" = "VANCO-FVF",
      "sm-form" = "VANCO-FF (SM)"
      )) %>% 
  group_by(genes, groups) %>% 
  summarise(mean_fold_change = mean(relative_fold_change)) %>% 
  ggplot(
    aes(x = groups,
        y = mean_fold_change,
        fill = groups)
  ) + 
  geom_col() +
  facet_wrap(~genes,
             ncol = 5, 
             scales = "free") +
  labs(title = "Level of gene expression in ileum tissue",
       y = "Gene expression relative fold change",
       x = "",
       fill = "Groups",
       caption = "Matrinem round 4") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="lightgrey"), # Change legend box background color
    plot.caption = element_text(color = "darkgrey", size=5)) + 
  scale_fill_brewer(palette="Set1")

bar_charts_all_genes

bar_charts_selected_genes <- delta_gene_expr %>% 
  filter(genes %in% c("TNFa","IL1b", "REG3G")) %>% 
  mutate(
    groups = recode_factor(  #Change the order of the groups to desired plot order
      groups,
      "con-bf"= "VANCO-BF",
      "fvt-form" = "VANCO-FVF",
      "sm-form" = "VANCO-SM"
      )) %>% 
  group_by(genes, groups) %>% 
  summarise(mean_fold_change = mean(relative_fold_change)) %>% 
  ggplot(
    aes(x = groups,
        y = mean_fold_change,
        fill = groups)
  ) + 
  geom_col() +
  facet_wrap(~genes,
             ncol = 5, 
             scales = "free") +
  labs(title = "Level of gene expression in ileum tissue - significant changes",
       y = "Gene expression relative fold change",
       x = "",
       fill = "Groups",
       caption = "Matrinem round 4") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="lightgrey"), # Change legend box background color
    plot.caption = element_text(color = "darkgrey", size=5)) + 
  scale_fill_brewer(palette="Set1")

bar_charts_selected_genes

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

# Gene expression in Matrinem Experiment 4

```{r}
delta_gene_expr <- read_excel("data/processed/gene_expression_fold_changes.xlsx") %>%
   mutate(
    groups = recode_factor(  #Change the order of the groups to desired plot order
      groups,
      "con-bf"= "VANCO-BF",
      "sm-form" = "VANCO-SM",
      "fvt-form" = "VANCO-FVF"

      ))
```

## Increased
```{r increased}
increased <- delta_gene_expr %>% 
 group_by(genes, groups) %>% 
  summarise(mean_fold_change = mean(relative_fold_change)) %>% 
  filter(mean_fold_change >= 1.75)
```

## Increased plot 
```{r increased plot}
increased_plot <- delta_gene_expr %>% 
  filter(genes %in% increased$genes) %>% 
  mutate(across(genes, factor, levels=c("TNFa","MUC1","IL1b","REG3G"))) %>%
  group_by(genes, groups) %>% 
  summarise(mean_fold_change = mean(relative_fold_change)) %>% 
  ggplot(
    aes(x = groups,
        y = mean_fold_change,
        fill = groups)
  ) + 
  geom_col() +
  facet_wrap(~genes,
             nrow = 1, 
             scales = "free") + 
  labs(
       y = "Fold Δ",
       x = "",
       fill = "Groups") +
  theme_bw()+
  theme(                   
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.position = "none") + 
    scale_fill_brewer(palette="Set1")
  increased_plot
```

## Decreased
```{r decreased}
decreased <- delta_gene_expr %>% 
 group_by(genes, groups) %>% 
  summarise(mean_fold_change = mean(relative_fold_change)) %>% 
  filter(mean_fold_change < 0.6)

@@

## Decreased plot
```{r decreased plot}
decreased_plot <- delta_gene_expr %>% 
  filter(genes %in% decreased$genes) %>% 
  #mutate(across(genes, factor, levels=c("MUC1","IL1b","REG3G"))) %>%
  group_by(genes, groups) %>% 
  summarise(mean_fold_change = mean(relative_fold_change)) %>% 
  ggplot(
    aes(x = groups,
        y = mean_fold_change,
        fill = groups)
  ) + 
  geom_col() +
  facet_wrap(~genes,
             nrow = 1, 
             scales = "free") + 
  labs(
       y = "Fold Δ",
       x = "",
       fill = "Groups") +
  theme_bw()+
  theme(                   
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.position = "none") + 
    scale_fill_brewer(palette="Set1")
decreased_plot
```

## No change 
```{r no change}
no_change <- delta_gene_expr %>% 
  filter(!genes %in% c(increased$genes, decreased$genes))
```

## No change plot 
```{r plot}
no_change_plot <- no_change %>% 
  group_by(genes, groups) %>% 
  summarise(mean_fold_change = mean(relative_fold_change)) %>% 
  ggplot(
    aes(x = groups,
        y = mean_fold_change,
        fill = groups)
  ) + 
  geom_col() +
  facet_wrap(~genes,
             nrow = 1, 
             scales = "free") +
  labs(
       y = "Fold Δ",
       x = "",
       fill = "Groups") +
  theme_bw()+
  theme(                   # Change the appearance of labels
    plot.title = element_text(color="darkgrey", size=12, face="bold"),
    axis.title.y = element_text(color="darkgrey", size=10, face="bold.italic"),
    axis.ticks.x = element_blank(),  # Hide labels
    axis.text.x = element_blank(),
    legend.title = element_text(face="bold"),   
    legend.position="bottom",
    legend.background = element_rect(fill="lightgrey"),
    plot.caption = element_text(color = "darkgrey", size=5)) + 
  scale_fill_brewer(palette="Set1")
```

## Patchwork
```{r}
in_de_no_patch <- (decreased_plot + increased_plot) / no_change_plot + plot_annotation(
  title = "Gene expression relative fold change",
  tag_levels = "A",
  tag_suffix = ')',
  caption = "A) Decreased relative expression.     B) Increased relative expression.     C) No change in gene expression."
) & 
  theme(plot.tag = element_text(size = 12),
        plot.caption = element_text(face = "bold"))
in_de_no_patch

### 2022-11-19 code/cytokines/Cytokines_serum.Rmd
progress

# Exp1
## Tissue weight 
```{r exp1_inspect data, echo=FALSE}

#_____Weight of tissue samples_____#
Exp1_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 1) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "CON-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 1",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with CON-BF as reference. \n
    **: p < 0.01, *: p < 0.05, NS: not significant."
  ) 
Exp1_tissue_weight
ggsave('exports/cytokines/Exp1-weights-of-tissue.png',Exp1_tissue_weight)
```

@@

Exp1_plot_all_cytokines
ggsave('exports/cytokines/Exp1-serum-adjusted-plot.png',Exp1_plot_all_cytokines)
```

>>>>

# Exp1

@@

Exp1_plot_all_cytokines
ggsave(width = 170, height = 120, units = "mm",'exports/cytokines/Exp1-serum-adjusted-plot.png',Exp1_plot_all_cytokines)
```

### 2022-11-19 code/cytokines/Cytokines_tissue_adjusted.Rmd
progress

---
title: "Cytokine analysis script - all rounds - adjusted for tissue weight"
author: "Kaare"
date: "11th October 2022"    
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

@@

#_____Weight of tissue samples_____#
Exp1_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 1) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "CON-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 1",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with CON-BF as reference. \n
    **: p < 0.01, *: p < 0.05, NS: not significant."
  ) 
Exp1_tissue_weight
ggsave('exports/cytokines/Exp1-weights-of-tissue.png',Exp1_tissue_weight)
```

@@

Exp1_tbl1 <- cytokines %>% 
  filter(exp_number == "1") %>%
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 1"
  ) %>%
  cols_width(label ~ px(80),
             stat_1 ~ px(140),
             stat_2 ~ px(140),
             stat_3 ~ px(140),
             stat_4 ~ px(140)) 
Exp1_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp1-tissue-adjusted.png", vwidth = 760, vheight = 450)

@@

Exp1_plot_all_cytokines
ggsave('exports/cytokines/Exp1-tissue-adjusted-plot.png',Exp1_plot_all_cytokines)
```

@@

#_____Weight of tissue samples_____#
Exp2_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 2) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "CON-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 2",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with CON-BF as reference. \n
    **: p < 0.01, *: p < 0.05, NS: not significant."
  ) 
ggsave('exports/cytokines/Exp2-weights-of-tissue.png',Exp2_tissue_weight)

@@

Exp2_tbl1 <- cytokines %>% 
  filter(exp_number == 2) %>%
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 2"
  ) 
Exp2_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp2-tissue-adjusted-table.png")

@@

Exp2_plot_all_cytokines
ggsave('exports/cytokines/Exp2-tissue-adjusted-plot.png',Exp2_plot_all_cytokines)
```

@@

#_____Weight of tissue samples_____#
Exp3_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 3) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "CON-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 3",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with CON-BF as reference. \n
    **: p < 0.01, *: p < 0.05, NS: not significant."
  ) 
ggsave('exports/cytokines/Exp3-weights-of-tissue.png',Exp3_tissue_weight)

@@

Exp3_tbl1 <- cytokines %>% 
  filter(exp_number == 3) %>%
  filter(group != "VANCO-BF") %>% 
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 3"
  ) 
Exp3_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp3-tissue-adjusted-table.png")
```

@@

Exp3_plot_all_cytokines
ggsave('exports/cytokines/Exp3-tissue-adjusted-plot.png',Exp3_plot_all_cytokines)
```

@@

#_____Weight of tissue samples_____#
Exp4_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 4) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "VANCO-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 4",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with VANCO-BF as reference. \n
    ****: p < 0.0005, ***: p < 0.001, NS: not significant."
  ) 
ggsave('exports/cytokines/Exp4-weights-of-tissue.png',Exp4_tissue_weight)

@@

Exp4_tbl1 <- cytokines %>% 
  filter(exp_number == 4) %>%
  #filter(group != "VANCO-BF") %>% 
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 4"
  ) 
Exp4_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp4-tissue-adjusted-table.png")
```

@@

Exp4_plot_all_cytokines
ggsave('exports/cytokines/Exp4-tissue-adjusted-plot.png',Exp4_plot_all_cytokines)
```

>>>>

---
title: "Cytokine analysis script - all rounds - adjusted for tissue weight"
author: "Kaare"
date: "11th October 2022"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```

@@

#_____Weight of tissue samples_____#
Exp1_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 1) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "CON-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 1",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with CON-BF as reference. \n
    **: p < 0.01, *: p < 0.05, NS: not significant."
  ) 
Exp1_tissue_weight
ggsave(width = 170, height = 120, units = "mm",'exports/cytokines/Exp1-weights-of-tissue.png',Exp1_tissue_weight)
```

@@

Exp1_tbl1 <- cytokines %>% 
  filter(exp_number == "1") %>%
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 1"
  ) %>%
  cols_width(label ~ px(80),
             stat_1 ~ px(140),
             stat_2 ~ px(140),
             stat_3 ~ px(140),
             stat_4 ~ px(140)) 
Exp1_tbl1
Exp1_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp1-tissue-adjusted-table.png")

@@

Exp1_plot_all_cytokines
ggsave(width = 170, height = 120, units = "mm", 'exports/cytokines/Exp1-tissue-adjusted-plot.png',Exp1_plot_all_cytokines)
```

@@

#_____Weight of tissue samples_____#
Exp2_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 2) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "CON-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 2",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with CON-BF as reference. \n
    **: p < 0.01, *: p < 0.05, NS: not significant."
  ) 
ggsave(width = 170, height = 120, units = "mm",'exports/cytokines/Exp2-weights-of-tissue.png',Exp2_tissue_weight)

@@

Exp2_tbl1 <- cytokines %>% 
  filter(exp_number == 2) %>%
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 2"
  ) 
Exp2_tbl1
Exp2_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp2-tissue-adjusted-table.png")

@@

Exp2_plot_all_cytokines
ggsave(width = 170, height = 120, units = "mm",'exports/cytokines/Exp2-tissue-adjusted-plot.png',Exp2_plot_all_cytokines)
```

@@

#_____Weight of tissue samples_____#
Exp3_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 3) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "CON-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 3",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with CON-BF as reference. \n
    **: p < 0.01, *: p < 0.05, NS: not significant."
  ) 
ggsave(width = 170, height = 120, units = "mm",'exports/cytokines/Exp3-weights-of-tissue.png',Exp3_tissue_weight)

@@

Exp3_tbl1 <- cytokines %>% 
  filter(exp_number == 3) %>%
  filter(group != "VANCO-BF") %>% 
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 3"
  ) 
Exp3_tbl1
Exp3_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp3-tissue-adjusted-table.png")
```

@@

Exp3_plot_all_cytokines
ggsave(width = 200, height = 120, units = "mm",'exports/cytokines/Exp3-tissue-adjusted-plot.png',Exp3_plot_all_cytokines)
```

@@

#_____Weight of tissue samples_____#
Exp4_tissue_weight <- cytokines_long %>%       
   filter(exp_number == 4) %>%
  ggplot(aes(x = group, y = tissue_weight_mg, fill = group)) + 
  geom_boxplot() +
  stat_compare_means(aes(label = ..p.signif..),
                   method = "wilcox.test", ref.group = "VANCO-BF",
                   label.y.npc = 0.55) +
  stat_compare_means(method = "kruskal.test",
    aes(label = paste0("Kruskal Wallis Test. \n p = ", ..p.format..)),
    label.y.npc = 0.75,
    label.x.npc = 0.3) +
  geom_point() +
  labs(
    title = "Tissue weight of intestinal samples, experiment 4",
    y = "Tissue weight (mg)",
    x = "",
    caption = "Pairwise comparison with VANCO-BF as reference. \n
    ****: p < 0.0005, ***: p < 0.001, NS: not significant."
  ) 
ggsave(width = 170, height = 120, units = "mm",'exports/cytokines/Exp4-weights-of-tissue.png',Exp4_tissue_weight)

@@

Exp4_tbl1 <- cytokines %>% 
  filter(exp_number == 4) %>%
  #filter(group != "VANCO-BF") %>% 
  select(group, INFg:TNFa) %>% 
  tbl_summary(by = group,
              digits = everything() ~ c(2,2,2),
              missing = "no",
              include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ #c("{mean} ({sd})",         
                                     "{median} ({p25}, {p75})") %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p() %>% 
  as_gt() %>%
  tab_header(title = md("**Tissue concentraions of proinflammatory cytokines** *(pg/ml/mg tissue)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "Matrinem Experiment 4"
  ) 
Exp4_tbl1
Exp4_tbl1 %>%
  gtsave(path = "exports/cytokines/", filename = "Exp4-tissue-adjusted-table.png")
```

@@

Exp4_plot_all_cytokines
ggsave(width = 170, height = 120, units = "mm",'exports/cytokines/Exp4-tissue-adjusted-plot.png',Exp4_plot_all_cytokines)
```
